### 2017-11-02 manuscript.rmd
small text modifications
fixed f_cdata row ordering

@@

####Overview grid of main binary traits
```{r ggtree_bin_heatmap, echo=F, message=F, warning=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=3)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(2,5:8)]
rownames(f_cdata) = rownames(cdata)
names(f_cdata)[4] = "Float"
gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1.6)
```

>>>>

Morphological character data were obtained from the literature, or from direct observation of available voucher material.

@@

####Overview grid of main binary traits
```{r ggtree_bin_heatmap, echo=F, message=F, warning=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=2.2)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(1,2,5:8,12)]
rownames(f_cdata) = rownames(cdata)
f_cdata[match(tree$tip.label,rownames(f_cdata)),]
names(f_cdata)[5] = "Float"
gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1)
```
